---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures"
)
```

# R package `SynDI`

# Synthetic Data Integration

`r badger::badge_devel("umich-biostatistics/SynDI", "blue")` `r badger::badge_code_size("umich-biostatistics/SynDI")`

## Overview

Regression inference for multiple populations by integrating summary-level data using stacked imputations. Gu, T., Taylor, J.M.G. and Mukherjee, B. (2021) Regression inference for multiple populations by integrating summary-level data using stacked imputations <arXiv:2106.06835>.

## Installation

If the devtools package is not yet installed, install it first:

```{r, eval = FALSE}
install.packages('devtools')
```

```{r, eval = FALSE}
# install the package from Github:
devtools::install_github('umich-biostatistics/SynDI', build_vignettes = TRUE) 
```

Once installed, load the package:

```{r, eval = FALSE}
library(SynDI)
```

## Example Usage

For examples, see the package vignettes:

```{r, eval = FALSE}
vignette("SynDI-example-binary")
vignette("SynDI-example-continuous")
```

### Current Suggested Citation

Gu, T., Taylor, J.M.G. and Mukherjee, B. (2021) Regression inference for multiple populations by integrating summary-level data using stacked imputations arXiv:2106.06835.
